Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-09-20 paper/main.tex
include discussion which was in previous sections in final discussion

\section{Conclusion (TODO)}
\label{section:conclusion}

>>>>

\textbf{Discussion on the Individual Treatment}\\
The individual treatment of the bacteria allows us in principle to estimate the distribution of the
parameters directly without having to resort to any assumptions on the form of said distribution.
This is true for any parameter, not just the growth rates, since we aim to estimate all mechanical
parameters of our cellular model.

The total parameter space $P$ is a product of all single spaces $P_i$ in which the parameters
$p_i$ live $P=P_0\times P_1\times\dots$ but some of these parameters share the same space (let's
assume $p_0,p_1\in \tilde{P}$).
This leaves the open question as to weather the optimization algorithm could be modified to leverage
this knowledge and obtain increased performance.
For instance, it might be valuable to initially consider individual parameters as globally defined
and start treating the individually after a certain amount of optimization steps.

\textbf{Discussion Identifiability and Model Reduction/Flexibility}\\
But it also shows that the approach which we used is able to detect these problems.
As we continue to develop these methods, we expect to be able to reuse many of the existing
theoretical approaches such as likelihood estimation and uncertainty quantification which have
already been developed extensively for less complex systems such as \acp{ode}.
\textbf{TODO citations, also: is this discussion?}
Fortunately, \texttt{cellular\_raza} was chosen to construct our model such that we are flexible in
changing the underlying representation if should find that such unidentifiabilities are structural
(model-based) rather than practical (due to lack of data).
This allows us to iterate and find the model formulation which suits the data best but still retain
the mechanistic methodology of our approach.

\section{Conclusion (TODO)}
